% Preamble
\documentclass[a4paper, 11pt]{scrreprt}
% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{acronym}
\usepackage{eurosym}
\usepackage{newtxmath,newtxtext}
%\usepackage{minted} %Must be before csquotes
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{float}
\usepackage{tocloft}
\usepackage{url}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=10mm,
top=10mm,
textwidth=190mm
}
\usepackage[style=authoryear,citestyle=authoryear,backend=bibtex]{biblatex}

\addbibresource{SysArchU2}

\setstretch{1.5}

\title{Exercise 2 — Image Processing Documentation}
\author{Matthias Rupp, Janik Mayr}
% Document
\begin{document}
\maketitle

\chapter{Start Instructions}
The program can be started with "java -jar <path>imageprocessing.jar <args>".
The table \ref{tab:args-table} shows the possible (and for jar-build required) arguments.
The arguments can be passed like the following: <name>=<value>
Example for minimal required input: java -jar imageprocessing.jar -src=loetstellen.jpg -exptCoords=expectedCentroids.txt
When no path is given in the respective arguments for the outputs (see table), the program will create a folder
imageprocessing/target in the folder where the jar is located. There, the reports.txt and the disks.png will be put.
\begin{table}[H]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|}
\hline
Name & Required & Definition & Default                                                        \\ \hline
-src & yes & Source image & Path: imageprocessing/src/main/resources/loetstellen.jpg       \\ \hline
-acc & / & Accuracy & 3                                                              \\ \hline
-pull & / & Switch to Pullpipe & false                                                          \\ \hline
-exptCoords & yes & File with expected Coords & Path: imageprocessing/src/main/resources/expectedCentroids.txt \\ \hline
-disksImgOut & / & Output for created DiskImg after Erosion & Path: imageprocessing/target/disks.png                         \\ \hline
-diskReportOut & / & Output for created Report & Path: imageprocessing/target/report.txt                        \\ \hline
-shapeTypeErode & / & Shape type for erode filter Range{[}0 - 3{]}       & 0                                                              \\ \hline
-kernelSizeErode & / & Kernel size for erode filter & 2                                                              \\ \hline
-kernelSizeMedian & / & Kernel size for median filter & 19                                                             \\ \hline
-removeFirstN & / & Removes the first n found disks in the given image & 1                                                              \\ \hline
\end{tabular}%
}
\caption{Table of command-line arguments}
\label{tab:args-table}
\end{table}
\chapter{Workflow Description}
The exercise is utilizing the OpenCV framework \parencite{intel_opencv_2019} and the maven artifact nu.pattern::opencv::2.4.9-4 to execute locally without OpenCV dll files installed.
The following workflow description follows the chronological steps of the process, which order of filters are represented by the pull pipe.
The source of the pipeline (Class: ImgSource) reads the passed file; converts the read image in an OpenCV matrix (Class: org.opencv.core.Mat) and exports a DataTransferObject DTO (Class: ImgDTO) containing the created matrix.
The first filter (Class: ROIFilter) virtually crops the image by creating a sub-matrix of the passed matrix, the selected area is refereed to as Region of Interest (ROI). Additionally the offset between the origin of the original matrix and the ROI matrix is saved for later.
To better distinguish between the disks and the background the second filter, a threshold filter (Class: ThresholdFilter) is used; the threshold type is Binary, Inverted.
The formula for the type \parencite{opencv_2.4.13.7_documentation_basic_nodate} projects every pixel form the src matrix grater then the threshold 30 to white and all other to black.
\[ dst(x, y) =
\begin{cases}
white       & \quad \text{if } src(x,y) > 30\\
black  & \quad \text{otherwise}
\end{cases}
\]
The result still contains noise, which can be minimized by a median blur filter (Class: MedianFilter). According to the OpenCV documentation \parencite{opencv_3.4.8_documentation_opencv:_nodate} each pixel is set to the median of its neighboring pixels.
The size in pixels for the neighbourhood is called kernel size.
The forth filter, a ErodeFilter (Class: ErodeFilter) removes the cables to the disk, by removing pixels not part of a structuring element.
The fifth filter (Class: Convert2JAIFilter) converts the the matrix into a PlanarImage and passes it with the ROI offsets to the given filter CalcCentroidsFilter and creates a DTO containing the provided coordinates (middle of the disks) and the input ImgDTO\@.
The sixth filter (Class: FilterFirstDisk) does not modify the images, but removes the fist n found centroids, this was done to match it to the size of expected centroids list.
The seventh filter (Class: QualityCheckFilter) checks if the detected coordinates are within the given accuracy and creates a report for each centroid with its results.
The eighth filter (Class: FindRadiusFilter) calculates the minimum and maximum radius of an enclosing circle for a centroid of an report.
Finally, the sink creates a file containing all information of the reports.

For the pull pipe, the SinkImpl is run and uses the same filters as the push pipe, only that the read method is used and
Readables are passed through the pipe.
The reason for the many casts in the MainPipes class is the fact that constructors for both Readables and Writeables were
overwritten, to enable us to create both a push- and a pull-pipe. Because of this, the Compiler can't tell which constructor
it should use, requiring the use of casts.
\printbibliography
\end{document}
